Methods to prioritise pop-up active transport infrastructure

### 2020-05-09 article.Rmd
Update prose

1. 'filtered permeability', e.g. as shown in [@salfordcitycouncil_salford_2020]

interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example 
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->
2. banning cars and to pedestrianise streets, greatly increasing the width of walkable space, New York's 'Open Streets' initiative being a prominent example [@litman_pandemicresilient_2020], and
3. the reallocation of one or more lanes of traffic to create pop-up cycleways, typically along arterial routes, with lanes reallocated using traffic cones in Auckland providing an early example [@orsman_covid_2020].

The focus of this article is on the third category.
In it we aim to answer the following research question:

>>>>

1. 'filtered permeability', e.g. as [shown](https://twitter.com/CatrionaSwanson/status/1258322956595453952) in [@salfordcitycouncil_salford_2020]

2. banning cars and to pedestrianise streets, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020]
3. the reallocation of one or more lanes on wide roads to create pop-up cycleways [@orsman_covid_2020]. 
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

The focus of this article is on the third category.
The research question is:
